{Supporting Information for 'Efficient Detection and Classification of Epigenomic Changes Under Multiple Conditions' by Pedro L. Baldoni$^*$, Naim U. Rashid$^*$, and Joseph G. Ibrahim$^*$}

### 2021-03-04 Latex/appendix/webappendix.Rnw
Fix reference

Finally, we used the estimated mixture model posterior probabilities $Pr(W_{jl}=1|Z_{j}=2,\mb{y}_{..j},\mb{x};\hat{\bs{\Psi}})$, $j=1,\ldots,M$, to classify the differential combinatorial patterns of enrichment of detected differential windows. To this end, we first calculated the maximum estimated mixture model posterior probability across all $L$ components to determine the most likely differential combinatorial pattern from genomic windows assigned to be part of the differential state. Then, we compared the window-based classification with the true window-based simulated states from the Markov Chain (states $2,\ldots,G-1$). In Figures~\ref{fig:sim1.fig1}-\ref{fig:sim1.fig3}, panel B shows the confusion matrices of classified (x-axis) and simulated (y-axis) differential windows for a scenario with three conditions. Differential combinatorial patterns of enrichment are represented by the sequences of letters 'E' (enrichment) and 'B' (background), such that each letter corresponds to the status of a given condition. The number of windows (averaged over a all simulated data sets) is shown as entries of the matrices and represented by the color scale. Darker colors on the diagonal entries indicate better agreement between simulated and classified patterns. By utilizing the posterior probabilities from the mixture model, we observed a good performance when classifying the differential combinatorial pattern of enrichment from differential windows. Results were best under scenarios with higher number of replicates or SNR.

>>>>

Finally, we used the estimated mixture model posterior probabilities $Pr(W_{jl}=1|Z_{j}=2,\mb{y}_{..j},\mb{x};\hat{\bs{\Psi}})$, $j=1,\ldots,M$, to classify the differential combinatorial patterns of enrichment of detected differential windows. To this end, we first calculated the maximum estimated mixture model posterior probability across all $L$ components to determine the most likely differential combinatorial pattern from genomic windows assigned to be part of the differential state. Then, we compared the window-based classification with the true window-based simulated states from the Markov Chain (states $2,\ldots,G-1$). In Figures~\ref{fig:sim1.fig1}-\ref{fig:sim1.fig2}, panel B shows the confusion matrices of classified (x-axis) and simulated (y-axis) differential windows for a scenario with three conditions. Differential combinatorial patterns of enrichment are represented by the sequences of letters 'E' (enrichment) and 'B' (background), such that each letter corresponds to the status of a given condition. The number of windows (averaged over a all simulated data sets) is shown as entries of the matrices and represented by the color scale. Darker colors on the diagonal entries indicate better agreement between simulated and classified patterns. By utilizing the posterior probabilities from the mixture model, we observed a good performance when classifying the differential combinatorial pattern of enrichment from differential windows. Results were best under scenarios with higher number of replicates or SNR.
